Testing Gravity Using Type Ia Supernovae Discovered by Next Generation Wide Field Imaging Surveys

### 2019-02-15 doc/article.tex
remove appendix
antilogus comments

\author{S.~Perlmutter}

@@

@@

%\begin{comment}
\newpage
We are interested in
$$F^{-1}_{00,\alpha} = \frac{F_{11,\alpha}}{F_{00}F_{11}-F_{01}^2} - \frac{F_{11}}{(F_{00}F_{11}-F_{01}^2)^2}\left(F_{00,\alpha}F_{11}+
F_{00}F_{11,\alpha} - 2 F_{01}F_{01,\alpha}\right).$$

@@

  \begin{align}
D_{,\Omega_M} & =\gamma D \int_a^1 \Omega_M^{\gamma-1} d\ln{a}\\
 f_{,\Omega_M} & = \gamma \Omega_M^{\gamma -1} \\
 \Omega_{M,\Omega_{M_0}} & =\frac{\Omega_{M_0}(1-a^3) + 2a^3-1}{(\Omega_{M_0}+(1-\Omega_{M_0}a^3))^2}
 \end{align}
%\end{comment}
%
%
%\begin{align}
%C^{-1}_{,s}  = &  \frac{1}{(P_{gg}(k,\mu) + \frac{1}{n_g})(P_{vv}(k,\mu) + s)- P_{vg}(k,\mu)^2}
% \begin{bmatrix}
%   1 &
%   0\\
%   0 &
%  0
%   \end{bmatrix}.\\
%  & -
% \frac{ P_{gg}(k,\mu) + \frac{1}{n_g} }{\left((P_{gg}(k,\mu) + \frac{1}{n_g})(P_{vv}(k,\mu) + s)- P_{vg}(k,\mu)^2\right)^2} \\
%& \times 
%     \begin{bmatrix}
%     P_{vv}(k,\mu) + s &
%   -P_{vg}(k,\mu)  \\
%  - P_{vg}(k,\mu)  &
%  P_{gg}(k,\mu) + \frac{1}{n_g} 
%   \end{bmatrix}.
% \end{align}

>>>>

\author{P.~Nugent}
\affiliation{Computational Research Division, Lawrence Berkeley National Laboratory, 
    1 Cyclotron Road, Berkeley, CA, 94720}\author{S.~Perlmutter}

@@

A search tailored to discover SN~Ia to a certain depth will also discover intrinsically fainter SNe~IIP to a shallower
redshifts.  Advances are being made to calibrate these SN distances, with a 0.2~mag distance modulus uncertainty seemingly feasable.
With a  $\sim 4.5$ higher number density than SNe~Ia   we project uncertainties in the growth index of
$\sigma_\gamma = 0.067, 0.046$ for  $z_{max}=0.05$, 2- and 10-year surveys respectively.  Including follow-up of
SNe~IIP witin a SN~Ia program could be beneficial, particularly for checks of systematics.

@@

\begin{comment}
\newpage
We are interested in
$$F^{-1}_{00,\alpha} = \frac{F_{11,\alpha}}{F_{00}F_{11}-F_{01}^2} - \frac{F_{11}}{(F_{00}F_{11}-F_{01}^2)^2}\left(F_{00,\alpha}F_{11}+
F_{00}F_{11,\alpha} - 2 F_{01}F_{01,\alpha}\right).$$

@@

  \begin{align}
D_{,\Omega_M} & =\gamma D \int_a^1 \Omega_M^{\gamma-1} d\ln{a}\\
 f_{,\Omega_M} & = \gamma \Omega_M^{\gamma -1} \\
 \Omega_{M,\Omega_{M_0}} & =\frac{\Omega_{M_0}(1-a^3) + 2a^3-1}{(\Omega_{M_0}+(1-\Omega_{M_0}a^3))^2}
 \end{align}
\end{comment}
%
%
%\begin{align}
%C^{-1}_{,s}  = &  \frac{1}{(P_{gg}(k,\mu) + \frac{1}{n_g})(P_{vv}(k,\mu) + s)- P_{vg}(k,\mu)^2}
% \begin{bmatrix}
%   1 &
%   0\\
%   0 &
%  0
%   \end{bmatrix}.\\
%  & -
% \frac{ P_{gg}(k,\mu) + \frac{1}{n_g} }{\left((P_{gg}(k,\mu) + \frac{1}{n_g})(P_{vv}(k,\mu) + s)- P_{vg}(k,\mu)^2\right)^2} \\
%& \times 
%     \begin{bmatrix}
%     P_{vv}(k,\mu) + s &
%   -P_{vg}(k,\mu)  \\
%  - P_{vg}(k,\mu)  &
%  P_{gg}(k,\mu) + \frac{1}{n_g} 
%   \end{bmatrix}.
% \end{align}
